Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-13 paper.tex
Add VAWT keyword
Define some more symbols

% Keywords: add 3 to 10 keywords
\keyword{Reynolds number; cross-flow turbine; turbine performance; marine
hydrokinetic energy; wind energy}

@@

The performance and wake characteristics of cross-flow (vertical-axis) turbines
depend on turbine solidity, blade profile (lift/drag, dynamic stall at reduced
frequency of turbine rotation, symmetry, thickness, camber), blade pitch, number
of blades, strut drag and operational parameters such as tip speed ratio---{\em
    and} on Reynolds number. Note that an average blade chord Reynolds number,
$Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$, can be expressed in terms
of tip speed ratio $\lambda \equiv \omega R/ U_\infty$; the value of $\lambda$
at which a turbine reaches peak performance is again a function of turbine
solidity $Nc/\pi D$.

>>>>

% Keywords: add 3 to 10 keywords
\keyword{Reynolds number; cross-flow turbine; turbine performance; marine
hydrokinetic energy; wind energy; VAWT}

@@

The performance and wake characteristics of cross-flow (vertical-axis) turbines
depend on turbine solidity, blade profile (lift/drag, dynamic stall at reduced
frequency of turbine rotation, symmetry, thickness, camber), blade pitch, number
of blades, strut drag and operational parameters such as tip speed ratio---{\em
    and} on Reynolds number. Note that an average blade chord Reynolds number,
$Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$, can be expressed in terms
of tip speed ratio $\lambda \equiv \omega R/ U_\infty$, where $U_\infty$ is the
free stream velocity, $c$ is the blade chord length, $\nu$ is the fluid
kinematic viscosity, $\omega$ is the rotor's angular velocity, and $R$ is the
rotor radius. The value of $\lambda$ at which a turbine reaches peak performance
is again a function of turbine solidity $Nc/\pi D$, which allows for the use of
a simpler Reynolds number based on turbine diameter $Re_D \equiv U_\infty
D/\nu$.
